MOMS-PI: Key dynamics

### 2021-12-17 notebook/_posts/2021-11-01-momspi-summary/momspi-summary.Rmd
Add MOMSPI regression analysis

```{r}
tmp1 <- momspi_cal %>%
  perturb(bias_all_vec, norm = "none") %>% 
  sample_sums %>%
  enframe('.sample', 'mean_efficiency')
tmp2 <- momspi_cal %>%
  filter_tax_table(.otu %in% control_species) %>%
  transform_sample_counts(close_elts) %>%
  perturb(bias_species %>% deframe, norm = "none") %>% 
  sample_sums %>%
  enframe('.sample', 'mean_efficiency_controls')
mean_eff <- left_join(tmp1, tmp2, by = '.sample') %>%
  left_join(sample_data(momspi_cal) %>% as_tibble, by = '.sample')
```

@@

```{r}
tmp <- top_species %>% 
  select(-.abundance) %>% 
  pivot_wider(names_from = type, values_from = .otu, 
    names_glue = 'top_{str_to_lower(type)}')
mean_eff1 <- mean_eff %>%
  left_join(genus_prop, by = '.sample') %>%
  left_join(tmp, by = '.sample') %>%
  mutate(
    top_plot = fct_lump_n(top_calibrated, 7)
  )
rm(tmp)
```

@@

>>>>

```{r}
tmp1 <- momspi_cal %>%
  perturb(bias_all_vec, norm = "none") %>% 
  sample_sums %>%
  enframe('.sample', 'mean_efficiency')
tmp2 <- momspi_cal %>%
  filter_tax_table(.otu %in% control_species) %>%
  transform_sample_counts(close_elts) %>%
  perturb(bias_species %>% deframe, norm = "none") %>% 
  sample_sums %>%
  enframe('.sample', 'mean_efficiency_controls')
mean_eff <- left_join(tmp1, tmp2, by = '.sample')
```

@@

```{r}
tmp <- top_species %>% 
  select(-.abundance) %>% 
  pivot_wider(names_from = type, values_from = .otu, 
    names_glue = 'top_{str_to_lower(type)}')
mean_eff1 <- mean_eff %>%
  left_join(sample_data(momspi_cal) %>% as_tibble, by = '.sample') %>%
  left_join(genus_prop, by = '.sample') %>%
  left_join(tmp, by = '.sample') %>%
  mutate(
    top_plot = fct_lump_n(top_calibrated, 7)
  )
rm(tmp)
```

@@

# Testing

how many subjects?

```{r}
cts <- momspi %>% sample_data %>% as_tibble %>% count(host_subject_id)
nrow(cts)
#> [1] 577
cts %>% pull(n) %>% summary
#>    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#>    1.00    2.00    3.00    3.39    4.00    9.00 
cts %>%
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1)
  # geom_dotplot(binwidth = 1)
```

577 subjects
